### 2022-11-08 doc/src/IOMMU.tex
Add Sv57 and Sv57x4 to list of RISC-V address translation modes
Signed-off-by: John Hauser <31252952+jhauser-us@users.noreply.github.com>

For RV64, the first doubleword of an MSI PTE in basic translate mode
has the same encoding as a regular {\RISCV} leaf PTE for Sv39, Sv48,
Sv39x4, or Sv48x4 page-based address translation, with PTE fields D, A,
G, U, and X all zeros and W~= R~=~1.
Hence, the MSI PTE's first doubleword appears the same as a regular
PTE that grants read and write permission (R~= W~=~1) but not execute
permissions (X~=~0).
This same-encoded regular PTE would translate an MSI write the same as
the actual MSI PTE, except that what would be the PTE's accessed (A),
dirty (D), and user (U) bits are all zeros.
An \mbox{IOMMU} needs to treat only these three bits differently for an MSI
PTE versus a regular RV64 leaf PTE.

>>>>

For RV64, the first doubleword of an MSI PTE in basic translate mode
has the same encoding as a regular {\RISCV} leaf PTE for Sv39, Sv48,
Sv57, Sv39x4, Sv48x4, or Sv57x4 page-based address translation,
with PTE fields D, A, G, U, and X all zeros and W~= R~=~1.
Hence, the MSI PTE's first doubleword appears the same as a regular
PTE that grants read and write permission (R~= W~=~1) but not execute
permissions (X~=~0).
This same-encoded regular PTE would translate an MSI write the same as
the actual MSI PTE, except that what would be the PTE's accessed (A),
dirty (D), and user (U) bits are all zeros.
An \mbox{IOMMU} needs to treat only these three bits differently for an MSI
PTE versus a regular RV64 leaf PTE.
